\LARGE \bf Efficient Sampling for Grasp Quality Evaluation on Gaussian Process Implicit Surface Representations [v-12 09-30-2014]

### 2014-10-01 paper.tex
added en tools

 In section \ref{sec:contact}, we look at how to sample from $p(\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$. Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))$ and present a novel visualization technique for the distribution on surface normals. Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution. 
 .
\subsection{Distribution on Contact Points}\label{sec:contact} 
We would like to find the distribution on contact point $\textbf{c}_i$. A contact point in terms of the GPIS and line of action model can be defined as the point, $t$, when the signed distance function is zero and no points before said point along the line have touched the surface. We express this as the following conditions \\

\begin{enumerate}
	\item $sd(\gamma(t)) = 0$
	\item $sd(\gamma(\tau)) > 0$ $\forall \tau \in [a,t)$
\end{enumerate}

We now formally derive the distribution on contact point $p(\textbf{c}_i)$ using these conditions.  
. 
The probability distribution along the line $\gamma(t)$ is given by:

@@

This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian. One could think of this as a marginalization of all other points in signed distance field except the line of action. We would like to find the distribution on contact point $\textbf{c}_i$, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.

>>>>

 In section \ref{sec:contact}, we look at how to sample from $p(\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$. Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))$ and present a novel visualization technique for the distribution on surface normals. Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution. 
 .
\subsection{Distribution on Contact Points}\label{sec:contact} 
We would like to find the distribution on contact point $\textbf{c}_i$. A contact point in terms of the GPIS and line of action model can be defined as the point, $t$, when the signed distance function is zero and no points before said point along the line have touched the surface. We express this as the following conditions:

\vspace{-2ex}
\begin{align}
 &sd(\gamma(t)) = 0 \label{eq:density_cond} \\
&sd(\gamma(\tau)) > 0, \: \forall \tau \in [a,t) \label{eq:cdf_cond}
\end{align}

We will now demonstrate how to efficiently sample from these distributions and then show what this implies formally.

The probability distribution along the line $\gamma(t)$ is given by:

@@

This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian. One could think of this as a marginalization of all other points in signed distance field except the line of action. To sample contact points, one can simply draw samples from Eq. \ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies conditions \ref{list:contact_cond}.

We would like to find the distribution on contact point $\textbf{c}_i$, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.
